---
title: "Sentiment analysis for Animal Crossing user reviews"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  render = "normal_print", echo = TRUE, cache=TRUE, message=FALSE, warning=FALSE)

options(width = 100)

library(tidyverse)
library(skimr)
library(tidymodels)
library(textrecipes)

# define my pallete
my_palette <-
  c(darkgrey = "#575965", grey = "#868d99", lightgrey = "#e2e2e2", yellow = "#f5cc5a", 
    white = "#fefefe", black = "#2e2528", black2 = "#0A0A0A", lighgrey2 = "#5b5b5b", green = "#3986A6")

scales::show_col(my_palette)

my_theme <-
  theme_bw() +
  theme(
      plot.background = element_rect(fill = my_palette[[3]]),
      panel.background = element_rect(fill= my_palette[[3]]),
      axis.line.x = element_line(colour = my_palette[[2]]),
      panel.border = element_blank(),
      panel.grid = element_blank()
  )

theme_set(my_theme)

update_geom_defaults("bar", list(fill = my_palette[9], colour = my_palette[9]))
update_geom_defaults("col", list(fill = my_palette[9], colour = my_palette[9]))

```

> "Disclaimer: This report was written more of a practice for me than giving actual analytic insights"
> 
> --- humble beginner

## About

This report will look to provide insights using data exploration and machine learning models on a [tidytuesday's **Animal Crossing - New Horizons**](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-05-05) data set. 

Its worth mentioning that I have never heard of Animal Crossing and I apologize if I had been ignoring. However, good news, after I am done with report, I would have topped up my knowledge about this. 

In my own understanding Animal Crossing is game where it gives users the ability to participate in a life like simulation. Like comparable games like Minecraft, you are given tools and enviroments for you to freely explore. 

Hence, like every product created for human consumption, this games allows for users to rate their experience. The title probably already spoiled it but you guessed it! We are going to look into the those user reviews and perform a sentiment analysis. 

## Data

We are going to use the `skimr` package to look at a comprehensive summary of the data

```{r }
user_reviews <- 
  readr::read_tsv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv")

skimr::skim_tee(user_reviews, skim_fun = skim_without_charts)

```

This data set is pretty straightforward. We see that each observation (or row) represent a review made by a user. In total we have 2999 review with ach observation giving information about the 

  - user_name: reviewer's username
  - text: the review's commentary
  - date: date of which the review was posted, looks like there's 2 months worth of reviews
  - grade: numeric rating given by the user with a range from 0 to 10


## Exploratory

Lets look at the outcome's variable distribution:

```{r fig.align='center'}

user_reviews %>% 
  count(grade) %>% 
  ggplot(aes(x = grade, y = n)) +
  geom_col()


```

Off the bat, the distribution of looks weird. Both tails are quite heavy. 

However, lets give this some thought. These are review grades, hence ask yourself how often do you leave a review and when you do, why did you do it?

Most answers would be they rarely leave grades and when they do its because of extreme events such as complains or over the top experience. Applying this logic, it make sense to see high density on either side of grade scale. 

Looking at the distribution, it wont be wise to try a model grades directly, especially that this is my first time. Rather, if we can turn this into a classification problem where we split the grades in to bad or good rating. Let's say that a rating below 7 is bad. 

```{r}

reviews_parsed <-
  user_reviews %>% 
  mutate(
    rating = case_when(
      grade > 7 ~ "good",
      TRUE ~ "bad"
    )
    )

```

We could do a lot more on explatory analysis, but my skills are still at its infancy (especially text mining). Hence, I think we have enough to move on to modeling. 

## Modeling

First, we will set a seed for reproducibilty. 

Then we will split the reviews into a train set and test set using stratified sampling. We use stratified sampling so that we have balanced proportion of good and bad ratings in both data sets. 

```{r}
# set the seed for reproducibilty
set.seed(123)

# stratified sampling so that we have balanced proportion of good and bad ratings in both data sets
review_split <- initial_split(reviews_parsed, strata = rating) 

# extract training data
review_train <- training(review_split)
review_test <- testing(review_split)

```

Now that we have our train set and test set, let look at their proportions of ratings

```{r fig.align = "center"}

# check the rating count in train and test set
review_train %>% 
  count(rating) %>% 
  mutate(prop = n / sum(n), split = "train") %>% 
  bind_rows(
    review_test %>% 
      count(rating) %>% 
      mutate(prop = n / sum(n), split = "test")
  ) %>% 
  select(split, rating, n, prop) %>% 
  ggplot(aes(x = rating, y = prop)) +
  geom_col() +
  facet_wrap(split~.)

```


Great, there's a good balance of ratings in both data sets. 

Next is data preprocessing. We will use `recipes` package for this, however since this project is text heavy, we will also use `textrecipes` package. 

```{r, include=FALSE}
# rmarkdown::render(paste0(here::here(), '/sentiment_analysis_animal_crossing/report.Rmd'), output_file = paste0(here::here(),'/sentiment_analysis_animal_crossing/README.md'), output_format = c("github_document"))
```

